---
title: "ESA4_Aaliyah_Roderer"
author: "Aaliyah Roderer"
date: "2024-05-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r package}
#Package installieren
install.packages("ggplot2", repos = "https://cran.rstudio.com") 

#Package laden
library(ggplot2)
```

## Irisdaten importieren

```{r Daten}
data("iris")
```


## Scatter Plot Part 1

make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors

```{r scatterplot}

library(ggplot2)

data("iris")

ggplot(data = iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) + ggtitle("Scatter Plot") +
  geom_point() + labs(x = "Sepal Length", y = "Sepal Width", color = "Species") + theme_minimal()

```

# Scatter Plot Part 1

Add regression line in

```{r regression line}

ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point() + geom_smooth(method = "lm", se = FALSE, color = "black") + ggtitle("Scatter Plot with Regression Line") + labs(x = "Sepal Length", y = "Sepal Width") + theme_minimal()

```

# Pearson correlation

calculate the Pearson correlation for this plot

```{r correlation}

correlation <- cor(iris$Sepal.Length, iris$Sepal.Width)
correlation

```

# Boxplot

make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors

```{r boxplot}

ggplot(data = iris, aes(x = Species, y = Petal.Width, color = Species)) + geom_boxplot() + ggtitle("Boxplot of Petal Width by Species") + labs(x = "Species", y = "Petal Width") + theme_minimal() + theme(legend.position="none")

```

## Histogram

make the histogram for Petal.Width with 3 species separately in x-axis in different colors

```{r histogram}

# ggplot(data = iris, aes(x = Petal.Width, fill = Species, color = Species)) + ggtitle("Histogram of Petal Width by Species") + geom_histogram(alpha = 0.5, position = "identity", bins = 50) + labs(x = "Petal Width", y = "Frequency")

ggplot(iris, aes(x = Petal.Width, fill = Species)) + geom_histogram(binwidth = 0.2, position = "identity", alpha = 0.5) + facet_wrap(~Species) + ggtitle("Histogram of Petal Width by Species") + labs(x = "Petal Width", y = "Frequency") 

```

## T-test

run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species

```{r t-test}

res <- t.test(Petal.Width ~ Species, data = iris, subset = (Species == "setosa" | Species == "virginica"))
print(res)

if (res$p.value < 0.05) {
  print("The difference in Petal Width between setosa and virginica species is statistically significant.")
} else {
  print("There is no statistically significant difference in Petal Width between setosa and virginica species.")
}

```    
